Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-25 paper/ms.tex
merge rv plot to manuscript

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities.}
		\label{fig:rvs}
	}
\end{figure}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities of \tn.}
		{\it Top:} RV measurements, with best-fit instrument offsets
    and jitter terms included.  The expected scatter from starspots
    based on $v\sin i$ and the photometric modulation amplitude is of
    order 300m$\,$s$^{-1}$.
		{\it Bottom:}
    RV measurements phased to the orbital ephemeris of \pn.  The
    planet is not detected.  The black line shows a circular
    Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:rvs}
	}
\end{figure}
